AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
polished and add references

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{AIR4children: Artificial Intelligence and Robotics for Children}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Open Source Projects in AI and Robotics}
The spirit of open source software since 19XX with the contributions 
of users of different skills made a culture of openly share code to make
more robust tools (i.e. firefox, ubuntu, etc). Much recently, something 
similar to software is happening for hardware. One example is the community 
for arduino that open-sourced diagrams, code and with a low-cost microcontroller
magaged to make wordwile impact. See ~\ref{tab:opensourceprojects}.

\subsection{[Open Source AI]}
[Section to describe open-source AI projects and related them to air4children].
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape template parameters}.
[Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
which essentially takes advantage of a huge datasets to train neural networks.
The great impact of DL in recent years is also because of improvements in 
hardware development and mainly because of open source tools and libraries \cite{matelabs2017}.
Additionally to that, there is a huge range of applications in areas such as robotics,
transportation, medicine and last but not least in education.
That said, we propose to use a raspberry pi, a $\pounds$30 board with
GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
and pi camera in order to create a simple low-cost educational robot 
where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
]

@@

%One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
%happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.

\subsection{[Open Source Robotics]}
[Section to describe open-source robotics projects and related them to air4children.]
[As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
template parameters}.
]

@@

Immediately following this sentence is the point at which
Table~\ref{tab:opensourceprojects} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.
\begin{table}
  \begin{tabular}{cc}
    \toprule
    Project name & Year of creation \\  %& Community\\
    \midrule
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 \\ %& - \\
    JPL Open Source Rover \cite{OSR:2018} & April 2018 \\%& - \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 \\ %& 50K used robots in >70 countries\\
  \bottomrule
\end{tabular}
\caption{Open source projects}
\label{tab:opensourceprojects}
\end{table}

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.
That said, in a first phase, AIR4CHILDREN project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the particpants. 
This inital phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open hardware and software}
Considering previous references from the open source community, or perhaps other emerging ones, of not only AI and Robotics but also the ones for hardware and software, AIR4Children is aiming to make its resources accesible to young audiences \cite{UNICEF2020}.
For instance, one additional goal of air4children is to build and to design low-cost education robots as a way to mitigate the hight prices of educational robots.
Our initial prototype called ro-bit can recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
Another example is otto robot, a DIY educational robot based on arduino, servomotors and a scratch like interface to program the robot (Fig \ref{fig:teaser} b).

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
  \label{fig:car}
\end{figure}

\subsection{Open teaching materials}
Considering the work of Maria Montessori who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}. 
That said, children must develop concentration to develop their learning skills. 
For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
It is through movement and repetition that the child gets experience, allowing him to internalize new concepts. 
One potential way to develip such skills is the help of activities in engigering and robotics. 
Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012}.
Engineering tasks in robotics allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork \cite{elkin2014}.
Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.

In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
For instance, Elkin et al. (2014) \cite{elkin2014} explained how Robotics can also provide a way to engage children in problem-solving. 
Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.

>>>>

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{AIR4children: Artificial Intelligence and Robotics for Children}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
  %\Description{}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Open Source Software and Hardware for AI and Robotics}
In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accesibilty to users were crucial to its success \cite{gaudeul2007}.
Then, in 1983 Richard Stallman, with the fustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the fredom to run, study, copy, and make modifcation of software \cite{stallman1985}.
That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S. Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.

In the last decade, another wave of scientific inovation has been emerging in the field of AI due to open source software framewoks (e.g. pytorch, tensorflow, etc.) and places to distrute these (e.g. GitHub, gitlab, bitbucket) \cite{matelabs2017}
However, little has been seen accross the fields of AI and Robotics. 
For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
With regards to Robotics, the JPL Open Source Rover, created by eingeerers at NASA and initially released in April 2018, is a good reference as it is designed with detialed instructiosn for contrutrions for high school students and beyond, and technical specifications, 3D models, ensmabled instructions are fully avaiable \cite{OSR:2018}.
Recently, engineers at NVIDIA in 2019, resleased nano JetBot as a affortable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}. 
That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educatianal and fun characteristcs.
Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establisment and cost.

%One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
%happy, sad, surprise, fear, anger and neutral \cite{ho2016, ruiz-garcia2016}.

%[Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
%which essentially takes advantage of a huge datasets to train neural networks.
%Additionally to that, there is a huge range of applications in areas such as robotics,
%transportation, medicine and last but not least in education.
%That said, we propose to use a raspberry pi, a $\pounds$30 board with
%GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
%and pi camera in order to create a simple low-cost educational robot 
%where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
%]

@@

@@

%Immediately following this sentence is the point at which
%Table~\ref{tab:opensourceprojects} is included in the input file; compare the
%placement of the table here with the table in the printed output of
%this document.

\begin{table}
  \begin{tabular}{ccc}
    \toprule
    Project & Established  & Cost\\
    \midrule
    JPL Open Source Rover \cite{OSR:2018} & April 2018  &  USD 2500.00 \\
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019  & EUROS 212.00    \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 &  EUROS 100.00  \\
    Robot at air4children & 2021 & EUROS 100.00  \\
  \bottomrule
\end{tabular}
\caption{Open source projects for educational AI and Robotics}
\label{tab:opensourceprojects}
\end{table}

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.

In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the particpants. 
This inital phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:teaser} b).

\subsection{Open teaching materials}
Propossing teaching materials be child-like oriented, air4children is adopting Montessori's education, who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children based on Montessori education with the aim to help children to internalise new concepts and to develop concentration on their learning skills through movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics with materials approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
  \label{fig:car}
\end{figure}
